Case Study: Gene Set Enrichment Analysis (Mouse Data Set)

### 2018-04-01 datasets/GSEA/gsea-human.Rmd
Remove ash,fdrreg from GSEA case studies

```{r runningBenckmark, message=FALSE}
## rename columns and prepare for benchmarking
res <- dplyr:::select(goRes, c("over_represented_pvalue", "numInCat")) %>%
    dplyr:::rename(pval = over_represented_pvalue, ind_covariate = numInCat)
res$pval <- pmin(res$pval, 1)

## generate default BenchDesign
bd <- initializeBenchDesign()

## run benchmark
if (!file.exists(bench_file)) {
    sGSEA <- buildBench(bd, res, ftCols = "ind_covariate")
    saveRDS(sGSEA, file = bench_file)
} else {
    sGSEA <- readRDS(bench_file)
}
```

>>>>

```{r setup-benckmark, message=FALSE}
## rename columns and prepare for benchmarking
res <- dplyr:::select(goRes, c("over_represented_pvalue", "numInCat")) %>%
    dplyr:::rename(pval = over_represented_pvalue, ind_covariate = numInCat)
res$pval <- pmin(res$pval, 1)

## generate default BenchDesign
bd <- initializeBenchDesign()
bd <- dropBMethod(bd, "ashs")
bd <- dropBMethod(bd, "scott-empirical")
bd <- dropBMethod(bd, "scott-theoretical")
```

We exclude `ashr`, `scott-theoretical` and `scott-empirical` from the analysis because
the necessary assumptions are not met in the current case study. Namely, effect sizes
and standard errors are not available for ASH, and the test statistics are not normally
distributed under the null and alternative, as required by Scott's FDR regression methods.

```{r run-benchmark}
if (!file.exists(bench_file)) {
    sGSEA <- buildBench(bd, res, ftCols = "ind_covariate")
    saveRDS(sGSEA, file = bench_file)
} else {
    sGSEA <- readRDS(bench_file)
}
```

### 2018-04-01 datasets/GSEA/gsea-mouse.Rmd
Add covLinePlots to GSEA case studies
Remove ash,fdrreg from GSEA case studies

```{r runningBenckmark, message=FALSE}
## rename columns and prepare for benchmarking
res <- dplyr::select(goRes, over_represented_pvalue, numInCat) %>%
    dplyr::rename(pval = over_represented_pvalue,
                  ind_covariate = numInCat) %>%
    dplyr::mutate(pval = pmin(pval, 1))

## generate default BenchDesign
bd <- initializeBenchDesign()

## run benchmark
if (!file.exists(bench_file)) {
    sGSEAMouse <- buildBench(bd, res, ftCols = "ind_covariate")
    saveRDS(sGSEAMouse, file = bench_file)
} else {
    sGSEAMouse <- readRDS(bench_file)
}
```

@@

Gene set size of overlaps.

```{r}
methods <- c( "lfdr", "ihw-a10", "bl-df03", "qvalue", "bh", "bonf" )
plotCovariateBoxplots(sGSEAMouse, alpha = 0.1, nsets = 4,
                      methods = methods, trans = log2, maxNum = 5)
```

>>>>

```{r setup-benckmark, message=FALSE}
## rename columns and prepare for benchmarking
res <- dplyr::select(goRes, over_represented_pvalue, numInCat) %>%
    dplyr::rename(pval = over_represented_pvalue,
                  ind_covariate = numInCat) %>%
    dplyr::mutate(pval = pmin(pval, 1))

## generate default BenchDesign
bd <- initializeBenchDesign()
bd <- dropBMethod(bd, "ashs")
bd <- dropBMethod(bd, "scott-empirical")
bd <- dropBMethod(bd, "scott-theoretical")
```

We exclude `ashr`, `scott-theoretical` and `scott-empirical` from the analysis because
the necessary assumptions are not met in the current case study. Namely, effect sizes
and standard errors are not available for ASH, and the test statistics are not normally
distributed under the null and alternative, as required by Scott's FDR regression methods.

```{r run-benchmark}
if (!file.exists(bench_file)) {
    sGSEAMouse <- buildBench(bd, res, ftCols = "ind_covariate")
    saveRDS(sGSEAMouse, file = bench_file)
} else {
    sGSEAMouse <- readRDS(bench_file)
}
```

@@

```{r}
covariateLinePlot(sGSEAMouse, alpha = 0.1, covname = "ind_covariate")
```
